A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-01-27 manuscript.Rmd
explain why pessimistic
fix spelling

We deem each concept necessary to archive longterm reproducibility.
However, which tools you use to implement this concepts are mere matter of taste and project requirements.
This tutorial will follow the recommendations of @Peikert2019 and utilizes Git for version control, RMarkdown for dynamic document creation, Make for dependency tracking and Docker for software management.
Their interplay is shown in Figure \@ref(fig:schematic).
At several points, we suggest other viable alternatives.

>>>>

We deem each concept necessary to archive longterm reproducibility.
However, which tools you use to implement these concepts are mere matter of taste and project requirements.
This tutorial will follow the recommendations of @Peikert2019 and utilizes Git for version control, RMarkdown for dynamic document creation, Make for dependency tracking, and Docker for software management.
Their interplay is shown in Figure \@ref(fig:schematic).
At several points, we suggest other viable alternatives.
